---
format: html
echo: false
warning: false
footer-left: "[MPPAW](https://mppaw.org/) 2025 Survey"
footer-right: '[<i class="bi bi-github"></i> Source Code](https://github.com/jtkulas/MPPAW25)'
---

```{r}
library(surveydown)
```

::: {.sd_page id=welcome}

![](mppaw.jfif)

# MPPAW Member Survey: Shaping Our Future Direction

## Introduction

MPPAW is at a crossroads. We're evaluating our programming and structure to determine if there is a viable path to increase member engagement. Your input will directly shape our priorities for the coming year. This survey should take about 10 minutes to complete.

```{r}
sd_next(label="Begin Survey")
```

:::

::: {.sd_page}

### Current Engagement & Value: 

```{r}
sd_question(
  type  = 'mc',
  id    = 'engage1',
  label = "How would you describe your current level of engagement with MPPAW?",
  option = c(
    'Very active (attend most events, volunteer regularly)'    = "5",
    'Moderately active (attend some events, occasional volunteering)' = "4",
    'Minimally active (attend rarely, no volunteering)'        = "3",
    'Not currently active but interested in re-engaging'       = "2",
    'Not currently active and unlikely to re-engage'           = "1"
  )
)
```

```{r}
sd_question(
  type  = 'mc_multiple',
  id    = 'engage2',
  label = "What initially motivated you to join MPPAW? (Select all that apply)",
  option = c(
    'Professional networking'                 = "networking",
    'Learning from expert speakers'           = "learning",
    'Career development opportunities'        = "development",
    'Mentorship (giving or receiving)'        = "mentorship",
    'Contributing to the applied psychology community'           = "contributing",
    'Student/early career support'            = "students",
    'Other'                                   = "other"
  )
)
```

```{r}
sd_question(
  type  = 'mc_multiple',
  id    = 'engage3',
  label = "Which of these factors, if any, have reduced your participation in MPPAW activities? (Select all that apply)",
  option = c(
    'Time constraints/busy schedule'                 = "constraints",
    "Event timing doesn't work for me"           = "timing",
    'Content not relevant to my current needs'        = "content",
    'Prefer online professional communities (LinkedIn, Reddit, etc.)'        = "communities",
    'Geographic distance/location issues'           = "distance",
    'Post-pandemic preference for virtual engagement -- Other priorities took precedence'            = "covid",
    "Events don't provide enough networking opportunity" = "networking",
    'Other'                                   = "other"
  )
)
```

```{r}
sd_next(next_page = 'page2')
```

:::

::: {.sd_page id=page2}

### Future Programming Priorities: 

Across the next three questions you'll be asked to rank your top 3 program formatting preferences:

```{r}
sd_question(
  type  = 'select',
  id    = 'top1',
  label = "Which of the following program formats would be **most** valuable to you? (Top choice)
",
  option = c(
    "Expanded mentorship program (structured mentor/mentee matching)" = "mentor",
    "Large annual networking event/conference"           = "network",
    "Quarterly intensive workshops (3-4 per year)"       = "workshop",
    "Career development events (panels, job fairs)"               = "development",
    "Special interest groups (small, focused topic groups)"       = "interest",
    "Community service/giving back projects"              = "giving",
    "Virtual networking sessions"                         = "virtual",
    "Professional development certification programs"     = "certification",
    "Other"                                               = "other"
  )
)
```

```{r}
sd_question(
  type  = 'select',
  id    = 'top2',
  label = "Which of the following program formats would be **second most** valuable to you? (second best choice)
",
  option = c(
    "Expanded mentorship program (structured mentor/mentee matching)" = "mentor",
    "Large annual networking event/conference"           = "network",
    "Quarterly intensive workshops (3-4 per year)"       = "workshop",
    "Career development events (panels, job fairs)"               = "development",
    "Special interest groups (small, focused topic groups)"       = "interest",
    "Community service/giving back projects"              = "giving",
    "Virtual networking sessions"                         = "virtual",
    "Professional development certification programs"     = "certification",
    "Other"                                               = "other"
  )
)
```

```{r}
sd_question(
  type  = 'select',
  id    = 'top3',
  label = "Which of the following program formats would be **third most** valuable to you? (third best choice)
",
  option = c(
    "Expanded mentorship program (structured mentor/mentee matching)" = "mentor",
    "Large annual networking event/conference"           = "network",
    "Quarterly intensive workshops (3-4 per year)"       = "workshop",
    "Career development events (panels, job fairs)"               = "development",
    "Special interest groups (small, focused topic groups)"       = "interest",
    "Community service/giving back projects"              = "giving",
    "Virtual networking sessions"                         = "virtual",
    "Professional development certification programs"     = "certification",
    "Other"                                               = "other"
  )
)
```

```{r}
sd_next()
```

:::

::: {.sd_page}

### Mentorship: 

The next 6 questions all regard the [MPPAW mentorship program](https://mppaw.org/mentoring).

```{r}
sd_question(
  type  = 'mc',
  id    = 'mentor1',
  label = "Would you be likely to participate as a *mentor*?",
  option = c(
    "Yes, definitely"                             = "definitely",
    "Yes, possibly depending on time commitment"  = "possibly",
    "No, but I might in the future"               = "future",
    "No"                                          = "no"
  )
)
```

```{r}
sd_question(
  type  = 'mc',
  id    = 'mentor2',
  label = "Would you be likely to participate as a *mentee*?",
  option = c(
    "Yes, definitely"                             = "definitely",
    "Yes, possibly depending on the match"        = "possibly",
    "No, but I might in the future"               = "future",
    "No"                                          = "no"
  )
)
```

```{r}
sd_question(
  type  = 'mc',
  id    = 'mentor3',
  label = "What mentoring time commitment works best for your schedule?",
  option = c(
    "1-3 months"                = "1",
    "3-6 months"                = "3",
    "6-12 months"               = "6",
    "Ongoing/flexible timing"    = "flex"
  )
)
```

```{r}
sd_question(
  type  = 'mc_multiple',
  id    = 'mentor4',
  label = "What mentoring structure do you prefer? (Select all that apply)",
  option = c(
    "One-on-one mentoring"                      = "1",
    "Small group mentoring (3-5 people)"        = "small",
    "Large group mentoring circles (6+ people)" = "large",
    "Peer-to-peer mentoring networks"           = "networks"
  )
)
```

```{r}
sd_question(
  type  = 'mc_multiple',
  id    = 'mentor5',
  label = "What level of mentoring formality works best for you? (Select all that apply)",
  option = c(
    "Structured program with set goals and milestones"        = "structured",
    "Semi-structured with some guidelines but flexibility"    = "semi",
    "Informal relationship-building and advice sharing"       = "informal",
    "Event-based networking opportunities"                    = "event"
  )
)
```

```{r}
sd_question(
  type  = 'mc_multiple',
  id    = 'mentor6',
  label = "What mentoring format(s) would you participate in? (Select all that apply)",
  option = c(
    "Virtual meetings only"                                   = "virtual",
    "In-person meetings only"                                 = "inperson",
    "Hybrid (combination of virtual and in-person)"           = "hybrid",
    "Asynchronous communication (email, messaging platforms)" = "asynch"
  )
)
```

```{r}
sd_next()
```

:::


::: {.sd_page id=end}

## End

This it the last page in the survey.

```{r}
sd_close()
```

:::
